---
title: "mixure models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, DT, plotly, sjlabelled)
survey <- read_spss("~/Documents/data/GSS2018.sav")
df <- read_rds("survey_data_class_predictions.rds")
```


## Plot table proportions by predicted class {1, 2} for each outcome variable and demographic variable

```{r, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

outcome_variables <-  c("ABINSPAY", "ABMEDGOV1", "ABHELP1", "ABHELP2", "ABHELP3", "ABHELP4", 
                        "ABMORAL", "ABSTATE1", "ABSTATE2")

demogrpahic_variables <- c("SEX", "RACE", "CLASS", "PARTYID")

```

<br>

### Prorportion of class membership prediction
- From the posterior distribution we get the probability for each respondent of being a member of a class. 
```{r, warning=FALSE, error=FALSE, message=FALSE}
survey %>% select(outcome_variables) %>%  get_label() 
```

<br>

### breakdown of class membership predictions
```{r, warning=FALSE, error=FALSE, message=FALSE}
df %>% group_by(class_prediction) %>%  
  count() %>%  
  ungroup() %>% 
  mutate(proportion = n/sum(n)) %>% 
  datatable()
```


<br>

```{r, warning=FALSE, error=FALSE, message=FALSE}
df %>% group_by(class_prediction) %>%  
  count_(outcome_variables) %>%  
  mutate(proportion = n/sum(n)) %>% 
  arrange(desc(proportion)) %>%  
  datatable()
```


<br>

### demographic variables value codes
```{r, warning=FALSE, error=FALSE, message=FALSE}
survey %>% select(demogrpahic_variables) %>%  get_labels() 
```

<br>

### predicted class memberhip by gender
```{r, warning=FALSE, error=FALSE, message=FALSE}
df %>% 
  group_by(class_prediction) %>% 
  count(SEX) %>% 
  ungroup() %>% 
  mutate(proportion = n/sum(n)) %>% 
  plot_ly(x = ~SEX, y = ~proportion, type = 'bar', colors=~class_prediction, name = ~class_prediction) %>% 
  layout(yaxis = list(title = 'Proportion', range=c(0,1)), barmode = 'group')

```


<br>

### predicted class memberhip by RACE
```{r, warning=FALSE, error=FALSE, message=FALSE}
df %>% 
  group_by(class_prediction) %>% 
  count(RACE) %>% 
  ungroup() %>% 
  mutate(proportion = n/sum(n)) %>% 
  plot_ly(x = ~RACE, y = ~proportion, type = 'bar', colors=~class_prediction, name = ~class_prediction) %>% 
  layout(yaxis = list(title = 'Proportion', range=c(0,1)), barmode = 'group')

```


<br>

### predicted class memberhip by CLASS
```{r, warning=FALSE, error=FALSE, message=FALSE}
df %>% 
  group_by(class_prediction) %>% 
  count(CLASS) %>% 
  ungroup() %>% 
  mutate(proportion = n/sum(n)) %>% 
  plot_ly(x = ~CLASS, y = ~proportion, type = 'bar', colors=~class_prediction, name = ~class_prediction) %>% 
  layout(yaxis = list(title = 'Proportion', range=c(0,1)), barmode = 'group')

```


<br>

### predicted class memberhip by PARTYID
```{r, warning=FALSE, error=FALSE, message=FALSE}
df %>% 
  group_by(class_prediction) %>% 
  count(PARTYID) %>% 
  ungroup() %>% 
  mutate(proportion = n/sum(n)) %>% 
  plot_ly(x = ~PARTYID, y = ~proportion, type = 'bar', colors=~class_prediction, name = ~class_prediction) %>% 
  layout(yaxis = list(title = 'Proportion', range=c(0,1)), barmode = 'stack')

```


